Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-11-14 limits/ms.tex
Updated kappa plots so that the color scale is consistent. Updated sigp plot. Modified density profile equation to avoid confusing variable names. Added missing citations.

Unfortunately, the lens equation and the arrival times alone are not enough to form a
closed volume in the solution space. We have not imposed any strong constraints
on the density even so much as to ensure that it is non-negative everywhere. We
must therefore provide additional linear constraints so that we only sample
physical models. The explicit implementation for these priors has been
explained in \cite{}, but can be summarized as
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope everywhere $\le 0$.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity is enforced.
\item The density is radially symmetric. (Optional)
\end{enumerate}

@@

In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
\beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
solution space polytope. Using the MCMC sampling strategy described in \cite{}
we uniformly sample this space. Collectively, the sampled models are referred
to as an ensemble $\E = \{\M_i\}$, where we usually generate $\sim$1000 models. We
will typically show the ensemble average $\Eavg$ in the plots to
follow.

@@

The galaxies were generated as three dimensional particle distributions as in \citet{2009MNRAS.395.1079D}. Each component follows the profile:
\begin{equation}
\rho(m) = \frac{M}{4\pi a^3}(3-\gamma){(m/a)^{-\gamma}(1 + m/a)^{\gamma-4}}
\label{Dehnen profile}
\end{equation}
where $m^2 = (x/a)^2 + (y/b)^2 + (z/c)^2$, with $[a,b,c] = ???$; $\gamma$ is the central density profile index; and $a$ is the scale radius. In the
case $\gamma=1$ (and in the limit of spherical symmetry), this is the Hernquist profile \citep{1990ApJ...356..359H}.  The four combinations of
profile indices are shown in \tabref{mock galaxy params}. {\bf JR. Need to add explanation of triaxial parameters here. Is the above density equation correct in fact?}

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ {\bf (Left)} Mock data distribution on coarse grid for Sdom/DMcuspy. {\bf (Right)} Recover ensemble average kappa distribution.
XXX: Mention log scale and 0== critical density.}
\label{2d mass reconstruction}
\end{figure*}

>>>>

Unfortunately, the lens equation and the arrival times alone are not enough to form a
closed volume in the solution space. We have not imposed any strong constraints
on the density even so much as to ensure that it is non-negative everywhere. We
must therefore provide additional linear constraints so that we only sample
physical models. The explicit implementation for these priors has been
explained in \cite{2008ApJ...679...17C}, but can be summarized as
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope everywhere $\le 0$.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity is enforced.
\item The density is radially symmetric. (Optional)
\end{enumerate}

@@

In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
\beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
solution space polytope. Using the MCMC sampling strategy described in \cite{2012MNRAS.425.3077L}
we uniformly sample this space. Collectively, the sampled models are referred
to as an ensemble $\E = \{\M_i\}$, where we usually generate $\sim$1000 models. We
will typically show the ensemble average $\Eavg$ in the plots to
follow.

@@

The galaxies were generated as three dimensional particle distributions as in
\citet{2009MNRAS.395.1079D}. Each component follows the profile:
%
\begin{equation} 
  \rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}} 
  \label{Dehnen profile} 
\end{equation} 
%
where $a$ is the component scale radius mentioned in \tabref{mock galaxy params},
$r^2 = (x/\lambda_1)^2 + (y/\lambda_2)^2 + (z/\lambda_3)^2$, and the axis
ratios are $\lambda_1:\lambda_2:\lambda_3 = 6:4:3$.
In the case where the central density profile index
$\gamma$ is unity (and in the limit of spherical symmetry), this is the Hernquist
profile \citep{1990ApJ...356..359H}.  The four combinations of profile indices
are shown in \tabref{mock galaxy params}. {\bf JR. Need to add explanation of
triaxial parameters here. Is the above density equation correct in fact?}

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ The mock data distribution for Sdom/DMcuspy on a coarse grid (left)
  and a typical recovered ensemble average $\kappa$ distribution. The contours are
  logarithmic values, where level 0 corresponds to the critical density.}
\label{2d mass reconstruction}
\end{figure*}
